### 2021-09-01 response_to_review.Rmd

- p19 l19 add ","

- p19 l19 be specific what is missing in current software, i.e., continue with "(such as ...)."

- p19 l23 perhaps "spaces" (there could be more than just one?)

- References
    - video library url needed - done
    - buja et al in wegman & solka add city - done
    - buja et al (1986) this is a conference proceedings series; capitalize similar to a journal, add page numbers - this probably needs to be fixed via bibstyle (no page numbers showing for proceeding entries)
    - chambers et al list the editors - I don't think there was any 'scientific' editor on this book, didn't find any relevant person to list here ...
    - coleman add when accessed - this was taken from animation package so I got the date when the rda file was added to its github repo and added it here...
    - cook et al (1995) adjust style (compare with previous reference) - done
    - cook et al (2018) remove the ArXiv information for an article that has been published - done
    - cook, swayne (2007) reference is wrong add add city of publication (New York, Berlin, Heidelberg?) - done
    - diaconis as above - either full journal names or abbreviations (adjust other references in a similar way, according to WIREs specifications) - done
    - fisher remove the first URL and just keep the one with the DOI - done
    - friedman is there a DOI? - added
    - horst capitalize both "A" as these seem to be geographic names; just "R package" once - fixed capitalization, but repetition needs to be fixed in bibstyle
    - hotelling should be "417-441" - fixed (plus full journal name instead of abbreviation)
    - huber is there a URL where this can be obtained? - could not find it via google at least...
    - laa et al (2020) section pursuit incomplete - fixed
    - laa et al (2021) burning sage incomplete - fixed
    - laa et al (2020) slice tour update reference (it is published now) and remove the arXiv information - fixed
    - lee at al DOI ? - added
    - li incomplete; use lower case "c" and "t" here - fixed
    - li where does the 5(3) come from? - check the web page again - fixed
    - martinez remove the first URL - fixed
    - mcinnes capitalize "UMAP" - fixed
    - moustafa incomplete; Remove the first URL - fixed
    - moustafa and hadi remove the first URL - fixed
    - nguyen capitalize P (in Python), R (in the next reference), etc. - fixed
    - pedersen just once; check gganimate capitalisation - fixed capitalisation, but repeating version number is bibstyle issue
    - sievert city?; should be "Chapman and Hall/CRC" (several times) - fixed
    - spyrison change to lower case (except R); 243-257 (again!) - fixed
    - sutherland et al DOI - added
    - swayne DOI - I have no idea why it is not printing the DOI for the XGobi reference...
    - swayne et al DOI; XGobi (as a software name); issue ? -fixed
    - tukey editors? - added something based on web search, but not sure I got the right names..
    - tukey pages, city, publisher ?; city? - as above ..
    - van der maaten they list this as 9(86) on their web page - fixed
    - wegman list editors only once; page numbers; is there a volume ? - these are Interface (conference proceedings) - problem with showing these information for proceedings entry, again bibstyle issue?
    - wilkinson capital "S" - fixed
    - xie lower case - fixed
    - you "R" - fixed
    - zhang extend reference as for other R packages; incomplete - fixed

### 2021-09-01 response_to_review.Rmd

   - **done**

- p19 l23 perhaps "spaces" (there could be more than just one?)

   - **done**

- References
    - video library url needed - done
    - buja et al in wegman & solka add city - done
    - buja et al (1986) this is a conference proceedings series; capitalize similar to a journal, add page numbers - this probably needs to be fixed via bibstyle (no page numbers showing for proceeding entries)
    - chambers et al list the editors - it seems there was no relevant editor to list here
    - coleman add when accessed - date added based on animation package (data was accessed through the package)
    - cook et al (1995) adjust style (compare with previous reference) - done
    - cook et al (2018) remove the ArXiv information for an article that has been published - done
    - cook, swayne (2007) reference is wrong add add city of publication (New York, Berlin, Heidelberg?) - done
    - diaconis as above - either full journal names or abbreviations (adjust other references in a similar way, according to WIREs specifications) - done
    - fisher remove the first URL and just keep the one with the DOI - done
    - friedman is there a DOI? - added
    - horst capitalize both "A" as these seem to be geographic names; just "R package" once - fixed capitalization, but repetition needs to be fixed via bibstyle
    - hotelling should be "417-441" - fixed (plus full journal name instead of abbreviation)
    - huber is there a URL where this can be obtained? - unfortunately not
    - laa et al (2020) section pursuit incomplete - fixed
    - laa et al (2021) burning sage incomplete - fixed
    - laa et al (2020) slice tour update reference (it is published now) and remove the arXiv information - fixed
    - lee at al DOI ? - added
    - li incomplete; use lower case "c" and "t" here - fixed
    - li where does the 5(3) come from? - check the web page again - fixed
    - martinez remove the first URL - fixed
    - mcinnes capitalize "UMAP" - fixed
    - moustafa incomplete; Remove the first URL - fixed
    - moustafa and hadi remove the first URL - fixed
    - nguyen capitalize P (in Python), R (in the next reference), etc. - fixed
    - pedersen just once; check gganimate capitalisation - fixed capitalisation, but repeating version number is bibstyle issue
    - sievert city?; should be "Chapman and Hall/CRC" (several times) - fixed
    - spyrison change to lower case (except R); 243-257 (again!) - fixed
    - sutherland et al DOI - added
    - swayne DOI - information is in the bib file but not showing (maybe bibstyle issue?)
    - swayne et al DOI; XGobi (as a software name); issue ? -fixed
    - tukey editors? - added
    - tukey pages, city, publisher ?; city? - added
    - van der maaten they list this as 9(86) on their web page - fixed
    - wegman list editors only once; page numbers; is there a volume ? - these are Interface (conference proceedings) - problem with showing these information for proceedings entry, again this appears to be a bibstyle issue
    - wilkinson capital "S" - fixed
    - xie lower case - fixed
    - you "R" - fixed
    - zhang extend reference as for other R packages; incomplete - fixed

### 2021-09-02 paper.Rmd
Fixed typos

A tour path, that is a sequence of projections, can be generated by geodesic interpolation between a set of target planes (Figure \ref{fig:tour-path}). Different methods for choosing target planes provide different tour paths. The grand tour [@Asimov1985-xr] is generated using randomly selected targets. A guided tour [@Cook1995-ae] generates targets as a sequence of interesting projections $A_i$ by applying projection pursuit optimization on a predefined criteria $c(\cdot)$ of ``interestingness'' of a projection, $argmax_A c(XA)$. A local tour (available originally in @Buja1986-la rocks back and forth from a particular plane $A$ to randomly chosen targets $A_i$ in a small neighborhood $\{A_j |\; d(A_j, A) < \epsilon \}$. A little tour (available originally in @McDonald1982-ht navigates through all of the coordinate planes,  e.g. in 2D this would correspond to all elements of $A$ are 0 except for one element in each column, $(A_{i1} = A_{j2} = 1, A_{k1} = A_{k2} = 0, ~~i, j, k = 1, ..., p, ~~i\neq j \neq k)$.

A manual tour [@cook_manual_1997] is the most different, because it effectively allows rotating from a projection where variable, $j$, is fully extended in one direction to another where it contributes nothing, i.e. $A[j] \in [0,1]; j=1, ..., p$. The contribution of all other variables is restricted by the initial projection used, and by the contribution of $A[j]$. The initial projection is typically the optimal projection found by the guided tour, and the manual tour is thus used to determine whether which variables are most important to the interesting structure seen.

@@

Note that, in the application of tours to understanding neural networks by @Li2020-kg} in Section \@ref(models) also has a manually controlled tour based on selecting and dragging individual points that they call the "the data point mode".

@@

The R package spinifex [@spyrison_spinifex_2020] has three primary features. It produces manual tours (predefined path or interactive manipulation, identifies orthonormal global feature bases with the use of the Rdimtools [@you_rdimtools_2020] package. It renders (manual or other) tours as animations exportable to static .gif (gganimate @pedersen_gganimate_2020 package) or interactive .html widgets (plotly @sievert_interactive_2020 package). Lastly it offers an interactive shiny application providing a graphical user interface to quickly explore different variables contribution to structure in the projection.

@@

Over the years there have been numerous applications of tours for problems solving. Here are a few examples. @Koschat-Swayne used the tour for telecommunication data to explore clustering of customers. @Symanzik2002NewAO used the image grand tour to detect locations of mines from satellite images, and traces of rock art beneath graffiti from photos. Census data is explored in @huh-kim. The multicollinearity between predictors in a large regression model on political preferences based on demographics is check with a tour by @forbes-cook-hyndman. Clustering is a common application for tours, and @newell-cook-hofmann-jannink discusses exploring clusters in population genetics of food crops. @macedo-cook-brown apply the grand tour to examine multiple climate variables in relation to their spatial coordinates.

>>>>

A tour path, that is a sequence of projections, can be generated by geodesic interpolation between a set of target planes (Figure \ref{fig:tour-path}). Different methods for choosing target planes provide different tour paths. The grand tour [@Asimov1985-xr] is generated using randomly selected targets. A guided tour [@Cook1995-ae] generates targets as a sequence of interesting projections $A_i$ by applying projection pursuit optimization on a predefined criteria $c(\cdot)$ of ``interestingness'' of a projection, $argmax_A c(XA)$. A local tour (available originally in @Buja1986-la rocks back and forth from a particular plane $A$ to randomly chosen targets $A_i$ in a small neighborhood $\{A_j |\; d(A_j, A) < \epsilon \}$. A little tour (available originally in @McDonald1982-ht) navigates through all of the coordinate planes,  e.g. in 2D this would correspond to all elements of $A$ are 0 except for one element in each column, $(A_{i1} = A_{j2} = 1, A_{k1} = A_{k2} = 0, ~~i, j, k = 1, ..., p, ~~i\neq j \neq k)$.

A manual tour [@cook_manual_1997] is the most different, because it effectively allows rotating from a projection where variable, $j$, is fully extended in one direction to another where it contributes nothing, i.e. $A[j] \in [0,1]; j=1, ..., p$. The contribution of all other variables is restricted by the initial projection used, and by the contribution of $A[j]$. The initial projection is typically the optimal projection found by the guided tour, and the manual tour is thus used to determine which variables are most important to the interesting structure seen.

@@

Note that, in the application of tours to understanding neural networks by @Li2020-kg in Section \@ref(models) also has a manually controlled tour based on selecting and dragging individual points that they call the "the data point mode".

@@

The R package spinifex [@spyrison_spinifex_2020] has three primary features. It produces manual tours (predefined path or interactive manipulation), identifies orthonormal global feature bases with the use of the Rdimtools [@you_rdimtools_2020] package. It renders (manual or other) tours as animations exportable to static .gif (gganimate @pedersen_gganimate_2020 package) or interactive .html widgets (plotly @sievert_interactive_2020 package). Lastly it offers an interactive shiny application providing a graphical user interface to quickly explore different variables contribution to structure in the projection.

@@

Over the years there have been numerous applications of tours for problems solving. Here are a few examples. @Koschat-Swayne used the tour for telecommunication data to explore clustering of customers. @Symanzik2002NewAO used the image grand tour to detect locations of mines from satellite images, and traces of rock art beneath graffiti from photos. Census data is explored in @huh-kim. The multicollinearity between predictors in a large regression model on political preferences based on demographics is checked with a tour by @forbes-cook-hyndman. Clustering is a common application for tours, and @newell-cook-hofmann-jannink discusses exploring clusters in population genetics of food crops. @macedo-cook-brown apply the grand tour to examine multiple climate variables in relation to their spatial coordinates.
